Supplementary Information

### 2021-01-13 doc/manuscript/MEE_manuscript.Rmd
references

Growth rates changed directionally for the majority (`r percent_sig_neg_trend_of_analyzed`, depending on growth metric) of site-species combinations that could be analyzed (Fig. `r year_fig`).
This finding was consistent with an independent analysis (Appendix `r decadal_analysis_appendix`, Figs. `r decadal_analysis_figs_all`) and corroborates a previous analysis from HKK showing decreases in $BAI$ over time [@nock_longterm_2011].
*(have there been analyses of this at any other sites?)*
Although $DBH$ and $year$ are difficult to disentangle [e.g., @peters_detecting_2015], decent coverage of $DBH$ x $year$ matrices for the species analyzed, together with general consistency across growth metrics and analysis methods (Appendix `r decadal_analysis_appendix`, Figs. `r year_fig`, `r decadal_analysis_figs_all`) suggest that our approach is generally reliable.
At a minimum, it provides a more appropriate alternative to two of the most commonly used methods for analyzing growth trends, conservative detrending and basal area correction [see @peters_detecting_2015], which would fail to capture the observed trends in $RW$ and $BAI$ with $DBH$ (Fig. `r size`).
For instance, based on our finding that $BAI$ tends to rise and fall with $DBH$, basal area correction would generally be biased towards finding positive trends for smaller trees and negative trends for larger trees.
Indeed, in a comparative analysis of methods to detect growth trends, @peters_detecting_2015 found that approach similar to ours ("regional curve standardization") to be among the most robust and recommended that future analyses take an approach very similar to that used here.

>>>>

Growth rates changed directionally for the majority (`r percent_sig_neg_trend_of_analyzed`, depending on growth metric) of site-species combinations that could be analyzed (Fig. `r year_fig`).
This finding was consistent with an independent analysis (Appendix `r decadal_analysis_appendix`, Figs. `r decadal_analysis_figs_all`) and corroborates previous analyses from HKK showing growth decreases over time [@nock_longterm_2011; @van_der_sleen_no_2015; @groenendijk_no_2015, but see @brienen_tree_2017].
*(have there been analyses of this at any other sites?)*
Although $DBH$ and $year$ are difficult to disentangle [e.g., @peters_detecting_2015; @brienen_tree_2017], decent coverage of $DBH$ x $year$ matrices for the species analyzed, together with general consistency across growth metrics and analysis methods (Appendix `r decadal_analysis_appendix`, Figs. `r year_fig`, `r decadal_analysis_figs_all`) suggest that our approach is relatively reliable, *albiet* still subject to the influence of some potential sampling and survivorship biases [@brienen_detecting_2012; @brienen_tree_2017], evaluation of which is beyond the scope of the current analysis.
At a minimum, it provides a more appropriate alternative to two of the most commonly used methods for analyzing growth trends, conservative detrending and basal area correction [see @peters_detecting_2015], which would fail to capture the observed trends in $RW$ and $BAI$ with $DBH$ (Fig. `r size`).
For instance, based on our finding that $BAI$ tends to rise and fall with $DBH$, basal area correction would generally be biased towards finding positive trends for smaller trees and negative trends for larger trees.
Indeed, in a comparative analysis of methods to detect growth trends, @peters_detecting_2015 found that approach similar to ours ("regional curve standardization") to be among the most robust and recommended that future analyses take an approach very similar to that used here.
